Augmentation of a Historical Harpsichord Keyboard Replica for Haptic-Enabled Interaction in Museum Exhibitions

### 2025-01-21 src/article.tex
Updates from Overleaf

Museums often face significant challenges in engaging visitors due to limitations in staffing and funding, which restrict the ways in which visitors can interact with collections \cite{Templeton2018, McAlpine2014}. For musical instrument museums, these challenges are compounded by the difficulty of preserving historical instruments in a playable condition \cite{McAlpine2014}. The instruments' inherent fragility and gradual decay inevitably result in a point where they can no longer be played. A significant cultural change has taken place in recent decades, shifting the focus from the playability of the originals to their conservation. Karp \cite{Karp1979,Karp1985} advocates for a deeper understanding of musical instruments so that enough knowledge is generated to make them as ``copyable'' as possible.

@@

Beyond enhancing the visitor experience, future design iterations will serve as a research tool to explore the unique characteristics of the harpsichord and its impact on performance through the \anona{ERC-funded NEMUS} project, aiming to virtually reproduce the sound of historical keyboard instruments, and upcoming projects such as Rem@ke \cite{remake1}.

@@

\subsection{Design Problem}\label{design-problem}

@@

\subsubsection{Design Constraints}\label{design-constraints}

@@

\subsection{Keyboard}\label{keyboard}

\subsubsection{Keyboard Construction}\label{keyboard-construction}
% PARAGRAPH FROM ROBERTO
The construction of the keyboard required three months of work to be fully completed
and followed the same construction phases as a real harpsichord.

@@

\begin{itemize}
\item
  Walnut wood for the wrestplank
\item
  Chestnut wood for the key levers
\item
  Boxwood and ebony for the key caps.
\item
  Cypress wood for the soundboard, a wood characterized by a
\item
  Beech wood, a brass spring and a seagull feather plectrum for the 98 jacks
\end{itemize}

@@

The model was designed to have two internal chambers a front and rear.
The front and back that was xxx by yyy by 370mm between the faceplate
and the jacks. The TONGUE THAT GOES INTO SLOT divides the chamber through
a small gap between the underside of the soundboard and the key guides.
The key guide needs to be deep enough to allow for the full movement of
the key and stop the key becoming unseated. The chamber then extends to
a support wall which divides the front and rear.

@@

\subsection{Prototyping}\label{prototyping}

\subsubsection{3-Key Prototype}\label{key-prototype}

\begin{itemize}
\item
  proof of concept
\item
  available on loan from museum
\item
  easy access to internal structure
\end{itemize}

\subsubsection{49-Key Prototype}\label{key-prototype-1}

For the final interface a 49-key (4-octave) was constructed by luthier
\anon{Roberto Livi}. The keyboard is in the same style† as the 3-key model with
to jacks per key.

The keyboard is fully enclosed and internally has two chambers, front
and rear, in which the electronics could be installed
\textbackslash figure(underside 49-key).

Keyboard to be used for exhibition at san colombano where it would be
available to play by general public.

Timescale: from initial discussion to delivery of interface to the \anon{NEMUS}
lab was 8-months. Active assembly of the instrument was 3 months

Constructed From:

\begin{itemize}
\item
  for exhibition
\item
  problems of scale
\item
  problems of timescale
\end{itemize}

\subsubsection{Sensor Criteria}\label{sensor-criteria}

@@

\subsubsection{Triggering a note}\label{triggering-a-note}

The message format covered in \textbackslash section

@@

\section{Electronics}\label{electronics}

@@

>>>>

Museums often face significant challenges in engaging visitors due to limitations in staffing and funding, which restrict the ways in which visitors can interact with collections \cite{Templeton2018, McAlpine2014}. For musical instrument museums, these challenges are compounded by the difficulty of preserving historical instruments in a playable condition \cite{McAlpine2014}. The instruments' inherent fragility and gradual decay inevitably result in a point where they can no longer be played, even when collections adhere to the strictest conservation protocols. A significant cultural change has taken place in recent decades, shifting the focus from the playability of the originals to their conservation. Karp \cite{Karp1979,Karp1985} advocates for a deeper understanding of musical instruments so that enough knowledge is generated to make them as ``copyable'' as possible.

@@

Beyond enhancing the visitor experience, future design iterations will serve as a research tool to explore the unique characteristics of the harpsichord and its impact on performance through the \anon{ERC-funded NEMUS} project, aiming to virtually reproduce the sound of historical keyboard instruments, and upcoming projects such as Rem@ke \cite{remake1}.

@@

\section{Design}

\section{Constraints}\label{design-problem}

@@

% \subsection{Design Constraints}\label{design-constraints}

@@

\subsection{Building the Model Keyboard}\label{keyboard}

% PARAGRAPH FROM ROBERTO
The construction of the keyboard required three months of work to be fully completed
and followed the same construction phases of a real harpsichord.

@@

\begin{itemize}
\item
  Walnut wood for the wrestplank
\item
  Chestnut wood for the key levers
\item
  Boxwood and ebony for the key caps.
\item
  Cypress wood for the soundboard
\item
  Beech wood, a brass spring and a seagull feather plectrum for the 98 jacks
\end{itemize}

@@

% The model was designed to have two internal chambers a front and rear.
% The front and back that was xxx by yyy by 370mm between the faceplate
% and the jacks. The TONGUE THAT GOES INTO SLOT divides the chamber through
% a small gap between the underside of the soundboard and the key guides.
% The key guide needs to be deep enough to allow for the full movement of
% the key and stop the key becoming unseated. The chamber then extends to
% a support wall which divides the front and rear.

@@

% \subsection{Prototyping}\label{prototyping}

% \subsubsection{3-Key Prototype}\label{key-prototype}

% \begin{itemize}
% \item
%   proof of concept
% \item
%   available on loan from museum
% \item
%   easy access to internal structure
% \end{itemize}

% \subsubsection{49-Key Prototype}\label{key-prototype-1}

% For the final interface a 49-key (4-octave) was constructed by luthier
% \anon{Roberto Livi}. The keyboard is in the same style† as the 3-key model with
% to jacks per key.

% The keyboard is fully enclosed and internally has two chambers, front
% and rear, in which the electronics could be installed
% \textbackslash figure(underside 49-key).

% Keyboard to be used for exhibition at san colombano where it would be
% available to play by general public.

% Timescale: from initial discussion to delivery of interface to the \anon{NEMUS}
% lab was 8-months. Active assembly of the instrument was 3 months

% Constructed From:

% \begin{itemize}
% \item
%   for exhibition
% \item
%   problems of scale
% \item
%   problems of timescale
% \end{itemize}

\section{Hardware Design}

\subsection{Sensor Criteria}\label{sensor-criteria}

@@

% \subsubsection{Triggering a note}\label{triggering-a-note}

% The message format covered in \textbackslash section

@@

% \section{Electronics}\label{electronics}

@@

\begin{figure}  
  \centering
  \includegraphics[,width=\linewidth]{src/images/exhibition-user-1.jpeg} 
  \caption{} 
  \Description{} 
  \label{fig:exhibition}
\end{figure}
